Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2018-09-13 Article.tex
Restructuration (2)
Passe partie 3 (avant lem 3.2.4)
Relecture partie 3 (avant prop. 3.2.7)
Relecture partie 3 (avant partie 3.3)
Relecture partie 3 (avant partie 3.3.2)
Relecture Partie 4 (debut)
MAJ
Relecture exemples Grassmann
Petites modifs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath,amsfonts,amssymb,amsthm,shuffle}
\usepackage[T1]{fontenc}
\usepackage[math]{anttor}

@@

\newcommand{\Cca}{\mathcal{C}}
\newcommand{\Oca}{\mathcal{O}}
\newcommand{\Afr}{\mathfrak{a}}
\newcommand{\Rfr}{\mathfrak{r}}
\newcommand{\Sfr}{\mathfrak{s}}
\newcommand{\Tfr}{\mathfrak{t}}
\newcommand{\BranchingTrees}{\mathfrak{P}}

@@

\newcommand{\FreeOperad}{\mathbf{F}}
\newcommand{\Mag}{\mathbf{Mag}}
\newcommand{\TwoMag}{2\Mag}
\newcommand{\KMag}{\K \Angle{\Mag}}
\newcommand{\QMag}{\mathcal{Q}\left(\KMag\right)}
\newcommand{\IMag}{\mathcal{I}\left(\KMag\right)}
\newcommand{\As}{\mathbf{As}}
\newcommand{\TwoAs}{2\As}
\newcommand{\CAsAll}{\mathbf{CAs}}
\newcommand{\CAs}[1]{\CAsAll^{\left(#1\right)}}
\newcommand{\KCAs}[1]{\K\CAs{#1}}
\newcommand{\KCAsAll}{\K\CAsAll}

\newcommand{\PrefixWord}{\mathrm{p}}
\newcommand{\Deg}{\mathrm{deg}}
\newcommand{\LComb}[1]{\mathfrak{c}^{\left(#1\right)}_{\diagup}}
\newcommand{\RComb}[1]{\mathfrak{c}^{\left(#1\right)}_{\diagdown}}
\newcommand{\LRank}{\mathrm{lr}}
\newcommand{\RBranch}{\mathrm{rb}}
\newcommand{\Catalan}{\mathrm{cat}}
\newcommand{\OrdQMag}{\preceq_{\mathrm{i}}}
\newcommand{\InfQMag}{\wedge_{\mathrm{i}}}
\newcommand{\SupQMag}{\vee_{\mathrm{i}}}
\newcommand{\LatQMag}{\left(\QMag,\OrdQMag,\InfQMag,\SupQMag\right)}
\newcommand{\OrdCAs}{\preceq_{\mathrm{d}}}
\newcommand{\InfCAs}{\wedge_{\mathrm{d}}}
\newcommand{\SupCAs}{\vee_{\mathrm{d}}}
\newcommand{\LatCAs}{\left(\CAsAll,\OrdCAs,\InfCAs,\SupCAs\right)}
\newcommand{\LatKCAs}{\left(\KCAsAll,\OrdCAs,\InfCAs,\SupCAs\right)}
\newcommand{\Unit}{\mathds{1}}
\newcommand{\Leaf}{\perp}
\newcommand{\Corolla}{\mathrm{c}}
\newcommand{\NormalForms}{\mathfrak{N}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\Compositions}{\mathcal{C}}

@@

\newcommand{\CongrCAs}[1]{\Congr^{(#1)}}

\newcommand{\Lightning}[1]{
\mathfrak{c}^{(#1)}_{\begin{tikzpicture}[scale=.1, Centering]
    \draw (0,0)--(-1,-2);
    \draw (-1,-2)--(0,-2);
    \draw (0,-2)--(-1,-4);
\end{tikzpicture}}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    We study quotients of the magmatic operad, that is the free
    nonsymmetric operad over one binary generator. In the linear
    setting, we show that the set of these quotients admits a lattice
    structure and we show an analog of the Grassmann formula for the
    dimensions of these operads. In the nonlinear setting, we define
    comb associative operads, that are operads indexed by nonnegative
    integers generalizing the associative operad. We show that the set
    of comb associative operads admits a lattice structure, isomorphic
    to the lattice of nonnegative integers equipped with the division
    order. Driven by computer experimentation, we provide a finite
    convergent presentation for the comb associative operad in
    correspondence with~$3$. Finally, we study quotients of the magmatic
    operad by one cubic relation by expressing their Hilbert series and
    providing combinatorial realizations.
\end{abstract}

@@

\tableofcontents

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Magmatic_operads}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Magmatic_quotient_three}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath,amsfonts,amssymb,amsthm,bm,shuffle}
\usepackage[T1]{fontenc}
\usepackage[math]{anttor}

@@

\newcommand{\Cca}{\mathcal{C}}
\newcommand{\Oca}{\mathcal{O}}
\newcommand{\Afr}{\mathfrak{a}}
\newcommand{\Rfr}{\mathfrak{r}}
\newcommand{\Sfr}{\mathfrak{s}}
\newcommand{\Tfr}{\mathfrak{t}}
\newcommand{\Zfr}{\mathfrak{z}}
\newcommand{\BranchingTrees}{\mathfrak{P}}

\newcommand{\LambdaB}{\bm{\lambda}}
\newcommand{\MuB}{\bm{\mu}}
\newcommand{\NuB}{\bm{\nu}}

@@

\newcommand{\FreeOperad}{\mathbf{F}}
\newcommand{\Mag}{\mathbf{Mag}}
\newcommand{\TwoMag}{2\Mag}
\newcommand{\KMag}{\K \Angle{\Mag}}
\newcommand{\KAs}{\K \Angle{\As}}
\newcommand{\QMag}{\mathcal{Q}\left(\KMag\right)}
\newcommand{\IMag}{\mathcal{I}\left(\KMag\right)}
\newcommand{\As}{\mathbf{As}}
\newcommand{\AAs}{\mathbf{AAs}}
\newcommand{\TwoNil}{2\mathbf{Nil}}
\newcommand{\RC}[1]{\mathbf{RC}^{\left(#1\right)}}
\newcommand{\KRC}[1]{\K\langle\RC{#1}\rangle}
\newcommand{\TwoAs}{2\As}
\newcommand{\CAsAll}{\mathbf{CAs}}
\newcommand{\CAs}[1]{\CAsAll^{\left(#1\right)}}
\newcommand{\KCAs}[1]{\K\langle\CAs{#1}\rangle}
\newcommand{\KCAsAll}{\K\langle\CAsAll\rangle}

\newcommand{\PrefixWord}{\mathrm{p}}
\newcommand{\Deg}{\mathrm{deg}}
\newcommand{\LComb}[1]{\mathfrak{c}^{\left(#1\right)}_{
\begin{tikzpicture}[xscale=.2,yscale=.17,Centering]
    \draw[Edge](0,0)--(-1,-1);
\end{tikzpicture}
}}
\newcommand{\RComb}[1]{\mathfrak{c}^{\left(#1\right)}_{
\begin{tikzpicture}[xscale=.2,yscale=.17,Centering]
    \draw[Edge](0,0)--(1,-1);
\end{tikzpicture}
}}
\newcommand{\LRank}{\mathrm{lr}}
\newcommand{\RBranch}{\mathrm{rb}}
\newcommand{\Catalan}{\mathrm{cat}}
\newcommand{\OrdQMag}{\preceq_{\mathrm{i}}}
\newcommand{\InfQMag}{\wedge_{\mathrm{i}}}
\newcommand{\SupQMag}{\vee_{\mathrm{i}}}
\newcommand{\LatQMag}{\left(\QMag,\OrdQMag,\InfQMag,\SupQMag\right)}
\newcommand{\OrdCAs}{\preceq_{\mathrm{d}}}
\newcommand{\InfCAs}{\wedge_{\mathrm{d}}}
\newcommand{\SupCAs}{\vee_{\mathrm{d}}}
\newcommand{\LatCAs}{\left(\CAsAll,\OrdCAs,\InfCAs,\SupCAs\right)}
\newcommand{\LatKCAs}{\left(\KCAsAll,\OrdCAs,\InfCAs,\SupCAs\right)}
\newcommand{\Unit}{\mathds{1}}
\newcommand{\Leaf}{{
\begin{tikzpicture}[xscale=.2,yscale=.22,Centering]
    \draw[Edge](0,0)--(0,-1);
\end{tikzpicture}
}}
\newcommand{\Corolla}{\mathrm{c}}
\newcommand{\NormalForms}{\mathfrak{N}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\Compositions}{\mathcal{C}}

@@

\newcommand{\CongrCAs}[1]{\Congr^{\left(#1\right)}}
\newcommand{\CongrRC}[1]{\Congr_{\left(#1\right)}}
\newcommand{\INiHil}{I_{\TwoNil}}
\newcommand{\IAs}{I_{\KAs}}
\newcommand{\IAAs}{I_{\AAs}}
\newcommand{\IRC}[1]{I_{\RC{#1}}}

\newcommand{\Lightning}[1]{
\mathfrak{c}^{\left(#1\right)}_{\begin{tikzpicture}[scale=.1, Centering]
    \draw[Edge](0,0)--(-1,-2);
    \draw[Edge](-1,-2)--(0,-2);
    \draw[Edge](0,-2)--(-1,-4);
\end{tikzpicture}}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    We study quotients of the magmatic operad, that is the free
    nonsymmetric operad over one binary generator. In the linear
    setting, we show that the set of these quotients admits a lattice
    structure and we show an analog of the Grassmann formula for the
    dimensions of these operads. In the nonlinear setting, we define
    comb associative operads, that are operads indexed by nonnegative
    integers generalizing the associative operad. We show that the set
    of comb associative operads admits a lattice structure, isomorphic
    to the lattice of nonnegative integers equipped with the division
    order. Driven by computer experimentations, we provide a finite
    convergent presentation for the comb associative operad in
    correspondence with~$3$. Finally, we study quotients of the magmatic
    operad by one cubic relation by expressing their Hilbert series and
    providing combinatorial realizations.
\end{abstract}

@@

\begin{small}
\tableofcontents
\end{small}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Mag_quotients}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{Cubic_quotients}
